---
title: "Max.WCST.R - A starter's package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wiscSortR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Max.WCST.R)
```

## What is `Max.WCST.R`?

`Max.WCST.R` provides tools to simulate and analyze the Wisconsin Card Sorting Task (WCST), a neuropsychological assessment designed to measure cognitive flexibility, abstract reasoning, and the ability to shift problem-solving strategies in response to changing rules.

The WCST is widely used in both research and clinical settings. It is particularly useful for assessing executive function deficits in individuals with:
- Schizophrenia
- Frontal lobe damage
- ADHD
- Autism Spectrum Disorder (ASD)
- Traumatic Brain Injury (TBI)
- Neurodegenerative disorders (e.g., Parkinson’s disease, dementia)

Performance on the WCST reflects a person's ability to detect and adapt to rule changes — a key component of executive functioning. High perseverative errors (repeating the same incorrect rule) often signal impairments in cognitive control.

The `Max.WCST.R` package enables simplified simulations of this task in R. It allows users to:
- Generate randomized card decks
- Run rule-shifting simulations with feedback
- Analyze session-level performance

This package is ideal for:
- Teaching executive function concepts
- Demonstrating rule-switching behavior
- Prototyping cognitive experiments

Generate a WCST Deck
You can generate a randomized deck of cards, each with a color, shape, and number:

```{r}
deck <- generate_wcst_deck(10)
head(deck)
```

Simulate a WCST Session
Run a full WCST session, where the rule changes after 6 consecutive correct answers:

```{r}
session <- simulate_wcst_session(n_trials = 15)
head(session)
```
Analyze the Results
Get summary statistics for a session, including accuracy and perseverative errors:

```{r}
analyze_wcst_results(session)
```

Full Example Workflow

```{r}
# Generate and simulate
deck <- generate_wcst_deck(20)
session <- simulate_wcst_session(20)

# Print session
print(session)

# Analyze session
analyze_wcst_results(session)
```

Extending wiscSortR

You can expand this package to:

Simulate different user strategies

Track performance over repeated sessions

Export data for experimental use
